saycam goldset analysis

### 2020-01-28 analysis/analysis_goldset.Rmd
update goldset code to check OP bounding boxes

### Code ot render out bounding boxes from OP on sample frames
```{r}
# # g_seg_info <- g_seg %>%
# #   distinct(full_image_path, vid_name_short, frame_ind)
# #   
# # bb_check <- bb %>%
# #   mutate(frame_ind = frame, vid_name_short = vid_name) %>%
# #   left_join(g_seg_info, by=c("vid_name_short","frame_ind")) %>%
# #   filter(!is.na(full_image_path)) %>%
# #   filter(mean_conf > 0)
# 
# # # dir.create(paste0('bbcheck/'))
# # unique_images <- bb_check$full_image_path[101:200]
# # 
# # for (image in unique_images){
# #   this_image_rgb <- image_read(image)
# #   img <- image_draw(this_image_rgb)
# #   a <- bb_check %>%
# #     filter(full_image_path %in% image) 
# #   
# #   # rect(a$x_pos, a$y_pos-a$height_y, a$x_pos+a$width_x, a$y_pos)
# #   text(a$center_x, a$center_y, a$center_y)
# #   
# #   annotated_file = paste0('bbcheck/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-center.jpg')
# #   image_write(img, annotated_file)
# #   dev.off()
# # }
```

>>>>

### Code ot render out bounding boxes from OP on sample frames
```{r}
g_seg_info <- g_seg %>%
  distinct(full_image_path, vid_name_short, frame_ind)

bb_check <- bb_all %>%
  mutate(frame_ind = frame, vid_name_short = vid_name) %>%
  left_join(g_seg_info, by=c("vid_name_short","frame_ind")) %>%
  filter(!is.na(full_image_path)) %>%
  filter(mean_confidence > 0)

# dir.create(paste0('bbcheck/'))
unique_images <- bb_check$full_image_path[300:350]

bb_check_face_tall <- bb_check_face %>%
  filter(top>.7) %>%
  filter(label=='face')

bb_check_weird_vids <- bb_check %>%
  filter(vid_name %in% weird_vids)

unique_images = unique(bb_check_weird_vids$full_image_path)
for (image in unique_images){
  this_image_rgb <- image_read(image)
  img <- image_draw(this_image_rgb)
  a <- bb_check %>%
    filter(full_image_path %in% image)

  # rect(a$x_pos, a$y_pos-a$height_y, a$x_pos+a$width_x, a$y_pos)

  text(a$left*680, a$top*480, a$top)

  annotated_file = paste0('bbcheck_sanity/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-center.jpg')
  image_write(img, annotated_file)
  dev.off()
}

face_check <- bb_check_weird_vids %>%
  filter(label=="face")
